Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-25 Paper/Paper.tex
ron comment on LLE added back

In an effort to visualize the span of the entire codebook, we used 
Locally linear embedding (LLE) \cite{Roweis2000}\footnote{implementation:
  \url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}}
to arrange the codewords on a 2D plane while keeping similar 
patterns as neighbors.  Figure \ref{fig:lle} shows the resulting 
distribution along with a sampling of patterns; notice trends such as the 
more ``wideband'' patterns to the right.

>>>>

In an effort to visualize the span of the entire codebook, we used 
Locally linear embedding (LLE) \cite{Roweis2000}\footnote{implementation:
  \url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}}
to arrange the codewords on a 2D plane while keeping similar 
patterns as neighbors.  Figure \ref{fig:lle} shows the resulting 
distribution along with a sampling of patterns; notice 
% ron's text instead of Dan
sustained
chords on the top left, chord changes on the bottom left, and more
complex sustained chords and ``wideband'' noisy patterns grouping to
the right of the figure.

%trends such as the 
%more ``wideband'' patterns to the right.
